Market simulator

### 2020-10-16 analysis/05_market_simulator.Rmd
figuring out how to upload new data to update the selected values

# Initial organization configuration
organization_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'org_data_test1.csv')
)

org_update <- reactiveValues(data = NULL)
org_update$data <- organization_data

@@

per_update <- reactiveValues(data = NULL)
per_update$data <- per_table

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_update$data[1:4,][which(org_update$data[1:4,2] == 1), 1]),
    width = "450px"
  )
})

# Issue area
selectInput(
  "org1_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Emergency response",
  selected = ifelse(
    sum(organization_data[5:7,2]) == 0, "Emergency response",
    as.character(organization_data[5:7,][which(organization_data[5:7,2] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org1_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data[8,2]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data[8,][which(organization_data[8,2] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org1_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data[9,2]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data[9,][which(organization_data[9,2] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org1_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data[10:11,2]) == 0, "Many small private donations",
    as.character(organization_data[10:11,][which(organization_data[10:11,2] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org1_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data[12:13,2]) == 0, "Friendly relationship with government",
    as.character(organization_data[12:13,][which(organization_data[12:13,2] == 1), 1])
  ),
  width = "450px"
)
```

@@

# Organization
selectInput(
  "org2_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data[1:4,][which(organization_data[1:4,3] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org2_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Environment",
  selected = ifelse(
    sum(organization_data[5:7,3]) == 0, "Emergency response",
    as.character(organization_data[5:7,][which(organization_data[5:7,3] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org2_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data[8,3]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data[8,][which(organization_data[8,3] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org2_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data[9,3]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data[9,][which(organization_data[9,3] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org2_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data[10:11,3]) == 0, "Many small private donations",
    as.character(organization_data[10:11,][which(organization_data[10:11,3] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org2_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data[12:13,3]) == 0, "Friendly relationship with government",
    as.character(organization_data[12:13,][which(organization_data[12:13,3] == 1), 1])
  ),
  width = "450px"
)
```

@@

```{r org3-inputs}
# Naming
textInput(
  "org3_name",
  label = "Organization Name:",
  value = "Organization 3",
  placeholder = "Enter Organization Name",
  width = "450px"
)

# Organization
selectInput(
  "org3_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data[1:4,][which(organization_data[1:4,4] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org3_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Human rights",
  selected = ifelse(
    sum(organization_data[5:7,4]) == 0, "Emergency response",
    as.character(organization_data[5:7,][which(organization_data[5:7,4] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org3_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data[8,4]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data[8,][which(organization_data[8,4] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org3_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data[9,4]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data[9,][which(organization_data[9,4] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org3_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data[10:11,4]) == 0, "Many small private donations",
    as.character(organization_data[10:11,][which(organization_data[10:11,4] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org3_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data[12:13,4]) == 0, "Friendly relationship with government",
    as.character(organization_data[12:13,][which(organization_data[12:13,4] == 1), 1])
  ),
  width = "450px"
)
```

@@

# Organization
selectInput(
  "org4_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data[1:4,][which(organization_data[1:4,5] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org4_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Refugee relief",
  selected = ifelse(
    sum(organization_data[5:7,5]) == 0, "Emergency response",
    as.character(organization_data[5:7,][which(organization_data[5:7,5] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org4_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data[8,5]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data[8,][which(organization_data[8,5] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org4_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data[9,5]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data[9,][which(organization_data[9,5] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org4_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data[10:11,5]) == 0, "Many small private donations",
    as.character(organization_data[10:11,][which(organization_data[10:11,5] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org4_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data[12:13,5]) == 0, "Friendly relationship with government",
    as.character(organization_data[12:13,][which(organization_data[12:13,5] == 1), 1])
  ),
  width = "450px"
)
```

@@

```{r import}
# Organization file input
fileInput(
  "file_org",
  "Import Organization Data",
  accept = c("text/csv",
             "text/comma-separated-values,text/plain",
             ".csv")
)

@@

observeEvent(eventExpr = input$org_apply, 
  handlerExpr = {
      req(input$file_org)
      file <- read_csv(input$file_org$datapath)
      org_update$data <- file
  }, ignoreNULL = FALSE)

>>>>

# Initial organization configuration
# organization_data <- read_csv(
#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
# )

organization_values <- reactiveValues()

organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_reactive <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_name = "organization_config01.csv"
    organization_values$file_type = "csv"
    organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  } else {
    organization_data <- read.csv(input$org_update$datapath)
    organization_values$file_name = input$org_update$name
    organization_values$file_size = input$org_update$size
    organization_values$file_type = input$org_update$type
    organization_values$file_path = input$org_update$datapath
  }
})

@@

# per_update <- reactiveValues(data = NULL)
# per_update$data <- per_table

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(organization_data()[1:4,][which(organization_data()[1:4,2] == 1), 1]),
    width = "450px"
  )

})

renderUI({

# Issue area
selectInput(
  "org1_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Emergency response",
  selected = ifelse(
    sum(organization_data$data[5:7,2]) == 0, "Emergency response",
    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org1_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org1_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org1_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org1_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
  ),
  width = "450px"
)

})
```

@@

renderUI({

# Organization
selectInput(
  "org2_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,3] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org2_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Environment",
  selected = ifelse(
    sum(organization_data$data[5:7,3]) == 0, "Emergency response",
    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,3] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org2_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data$data[8,3]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data$data[8,][which(organization_data$data[8,3] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org2_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data$data[9,3]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data$data[9,][which(organization_data$data[9,3] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org2_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data$data[10:11,3]) == 0, "Many small private donations",
    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,3] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org2_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data$data[12:13,3]) == 0, "Friendly relationship with government",
    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,3] == 1), 1])
  ),
  width = "450px"
)
})
```

@@

```{r org3-inputs}
# Naming
textInput(
  "org3_name",
  label = "Organization Name:",
  value = "Organization 3",
  placeholder = "Enter Organization Name",
  width = "450px"
)
renderUI({

# Organization
selectInput(
  "org3_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,4] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org3_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Human rights",
  selected = ifelse(
    sum(organization_data$data[5:7,4]) == 0, "Emergency response",
    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,4] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org3_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data$data[8,4]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data$data[8,][which(organization_data$data[8,4] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org3_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data$data[9,4]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data$data[9,][which(organization_data$data[9,4] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org3_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data$data[10:11,4]) == 0, "Many small private donations",
    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,4] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org3_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data$data[12:13,4]) == 0, "Friendly relationship with government",
    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,4] == 1), 1])
  ),
  width = "450px"
)
})
```

@@

renderUI({

# Organization
selectInput(
  "org4_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,5] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org4_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Refugee relief",
  selected = ifelse(
    sum(organization_data$data[5:7,5]) == 0, "Emergency response",
    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,5] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org4_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data$data[8,5]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data$data[8,][which(organization_data$data[8,5] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org4_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data$data[9,5]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data$data[9,][which(organization_data$data[9,5] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org4_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data$data[10:11,5]) == 0, "Many small private donations",
    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,5] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org4_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data$data[12:13,5]) == 0, "Friendly relationship with government",
    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,5] == 1), 1])
  ),
  width = "450px"
)
})
```

@@

```{r import}
# Organization file input
fileInput(
  "org_update",
  "Import Organization Data",
  accept = c("text/csv",
             "text/comma-separated-values,text/plain",
             ".csv")
)

@@

observeEvent(eventExpr = input$org_apply,
  handlerExpr = {
      req(input$org_update)
      file <- read_csv(input$org_update$datapath)
      org_update$data <- file
  }, ignoreNULL = FALSE)
